---
title: "Partial Correlation Network"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
<style type="text/css">

body{ /* Normal  */
      font-size: 12px;
  }
td {  /* Table  */
  font-size: 10px;
}

h1.title {
  font-size: 38px;
  color: DarkRed;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
    font-size: 22px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 18px;
  font-family: "Times New Roman", Times, serif;
  color: DarkBlue;
}
code.r{ /* Code block */
    font-size: 10px;
}
pre { /* Code block - determines code spacing between lines */
    font-size: 10px;
}
</style>
```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

getwd()

load(file = 'parcial.RData')
load(file = 'statsclusters.RData')

set.seed(123)

```

## Description

In the following graphs, each node represents a Phewas Code (>2% prevalence in our dataset) and associations between nodes are represented as edges. Association show unregulated partial correlations. For layout, codes with less strengths and less connections are placed further apart and those with more and/or stronger connections are placed closer to each other.

```{r, warning=FALSE}
library(qgraph)
library(igraph)

corMat <- cor(parcial, use = "pairwise.complete.obs") # Correlate data

Names<- statsclusters[1,1:(ncol(statsclusters)-3)]
# Unregularized partial correlation network
Graph_pcor <-
  qgraph(
    corMat,
    graph = "pcor",
    layout = "spring",
    threshold = "bonferroni",
    sampleSize = nrow(parcial),
    alpha = 0.05,
    vsize = 4,
    label.scale = TRUE,
    label.prop = 0.9,
    label.norm = "OOOO",
    labels = row.names(corMat),
    legend = FALSE,
    #legend.cex = 0.3,
    nodeNames = Names,
    palette="rainbow"
  )

# this code construct the connected components of the graph in list cluslabels
ig<-as.igraph(Graph_pcor, attributes = TRUE)
cl<-clusters(ig)
pos<-which(cl$csize>1)

clus<-list()
cluslabels<-list()

for (i in 1:length(pos)) {
  clus[[i]]<-which(cl$membership==pos[i])
  cluslabels[[i]]<-V(ig)$label[clus[[i]]]
}

Grnames=c(rep("Other",ncol(parcial)))
for (i in 1:length(cluslabels)) {
  for (j in 1:length(cluslabels[[i]])) {
    pos<-which(colnames(parcial)==cluslabels[[i]][j])
    Grnames[pos]<-paste("cluster",i,sep=" ")
  }
}
```

```{r, warning=FALSE}
# Unregularized partial correlation network
Graph_pcor <-
  qgraph(
    corMat,
    graph = "pcor",
    layout = "spring",
    threshold = "bonferroni",
    sampleSize = nrow(parcial),
    alpha = 0.05,
    vsize = 4,
    label.scale = TRUE,
    label.prop = 0.9,
    label.norm = "OOOO",
    labels = row.names(corMat),
    legend = TRUE,
    legend.cex = 0.4,
    legend.mode="groups",
    #GLratio=0.8,
    #layoutScale=c(1,4),
    nodeNames = Names,
    palette="rainbow", 
    groups=Grnames
    )

n<-vector()
for (i in 1:ncol(Names))
  n<-c(n,paste(Names[1,i],"(",rownames(corMat)[i],")",sep=""))

d<-data.frame(PhewasCode=n,cluster=Grnames)
#d$meaning<-n

##ordenamos
leyenda<-d[order(d$cluster),]

#guardamos
save(Graph_pcor, file= paste(directory,'/R/Graph_pcor.RData',sep = ""))

##imprimimos
library(printr) 
knitr::kable(leyenda, caption = 'legend for the clustered correlation network')
```


## Estimation of a regularized PCN using LASSO (tuning=0.50) 
```{r, warning=FALSE}
set.seed(123)
Graph_lasso <-
  qgraph(
    corMat,
    graph = "glasso",
    layout = "spring",
    tuning = 0.50,
    sampleSize = nrow(parcial),
    vsize = 4,
    label.scale = TRUE,
    label.prop = 0.9,
    label.norm = "OOOO",
    labels = row.names(corMat),
    legend = FALSE,
    legend.cex = 0.3,
    nodeNames = Names
    )


# this code construct the connected components of the graph in list cluslabels
ig<-as.igraph(Graph_lasso, attributes = TRUE)
cl<-clusters(ig)
pos<-which(cl$csize>1)

clus<-list()
cluslabels<-list()

for (i in 1:length(pos)) {
  clus[[i]]<-which(cl$membership==pos[i])
  cluslabels[[i]]<-V(ig)$label[clus[[i]]]
}

Grnames=c(rep("Other",ncol(parcial)))
for (i in 1:length(cluslabels)) {
  for (j in 1:length(cluslabels[[i]])) {
    pos<-which(colnames(parcial)==cluslabels[[i]][j])
    Grnames[pos]<-paste("cluster",i,sep=" ")
  }
}
set.seed(123)
Graph_lasso <-
  qgraph(
    corMat,
    graph = "glasso",
    layout = "spring",
    tuning = 0.50,
    sampleSize = nrow(parcial),
    vsize = 4,
    label.scale = TRUE,
    label.prop = 0.9,
    label.norm = "OOOO",
    labels = row.names(corMat),
    legend = TRUE,
    legend.mode="groups",
    legend.cex = 0.3,
    nodeNames = Names,
    palette="rainbow",
    groups=Grnames
    )

n<-vector()
for (i in 1:ncol(Names))
  n<-c(n,paste(Names[1,i],"(",rownames(corMat)[i],")",sep=""))

d<-data.frame(PhewasCode=n,cluster=Grnames)
#d$meaning<-n

##ordenamos
leyenda<-d[order(d$cluster),]

#guardamos
save(Graph_lasso, file= paste(directory,'/R/Graph_lasso.RData',sep = ""))

##imprimimos
library(printr) 
knitr::kable(leyenda, caption = 'legend for the clustered correlation network LASSO')
```

##This execution removes hipertension (401.1) and use Ising network estimation
```{r, warning=FALSE}
# Si queremos hacerlo con datos binarios. Después de esto habría que quitar la hipertensión (col.41)
library("bootnet")
Data_binary <- na.omit(parcial)
for (i in 1:ncol(Data_binary)){
  Data_binary[,i] <- 1 * (Data_binary[,i] > median(Data_binary[,i]))
}

#remove hipertension
Data_binary[,"401.1"]<-NULL
labels_bin<-row.names(corMat)
labels_bin<-labels_bin [! labels_bin %in% "401.1"]
names_bin<-Names
names_bin[,"401.1"]<-NULL

#Regularized Ising network estimation. LASSO regularization and EBIC model selection:

library("IsingFit")
Res <- IsingFit(as.matrix(Data_binary),family='binomial', gamma = 0.25, plot=FALSE,progressbar = FALSE)
Graph_Ising2 <- qgraph(
  Res$weiadj,
  layout = "spring",
  vsize = 4,
  label.scale = TRUE,
  label.prop = 0.9,
  label.norm = "OOOO",
  labels = labels_bin ,
  legend = FALSE,
  legend.cex = 0.4,
  legend.mode="groups",
  nodeNames = names_bin,
  palette="pastel" 
  #groups=Grnames
  )

# this code construct the connected components of the graph in list cluslabels
ig<-as.igraph(Graph_Ising2, attributes = TRUE)
cl<-clusters(ig)
pos<-which(cl$csize>1)

clus<-list()
cluslabels<-list()

for (i in 1:length(pos)) {
  clus[[i]]<-which(cl$membership==pos[i])
  cluslabels[[i]]<-V(ig)$label[clus[[i]]]
}

Grnames<-c(rep("Other",ncol(Data_binary)))
for (i in 1:length(cluslabels)) {
  for (j in 1:length(cluslabels[[i]])) {
    pos<-which(colnames(Data_binary)==cluslabels[[i]][j])
    Grnames[pos]<-paste("cluster",i,sep=" ")
  }
}

Graph_Ising2 <- qgraph(
  Res$weiadj,
  layout = "spring",
  vsize = 4,
  label.scale = TRUE,
  label.prop = 0.9,
  label.norm = "OOOO",
  labels = labels_bin ,
  legend = TRUE,
  legend.cex = 0.4,
  legend.mode="groups",
  nodeNames = names_bin,
  palette="pastel",
  groups=Grnames
  )


n<-vector()
for (i in 1:ncol(names_bin))
  n<-c(n,paste(names_bin[1,i],"(",rownames(Data_binary)[i],")",sep=""))

d<-data.frame(PhewasCode=n,cluster=Grnames)
#d$meaning<-n

##ordenamos
leyenda<-d[order(d$cluster),]

#guardamos
save(Graph_Ising2, file= paste(directory,'/R/Graph_Ising2.RData',sep = ""))

##imprimimos
library(printr) 
knitr::kable(leyenda, caption = 'legend for the clustered correlation network LASSO/EBIC without hipertension')

```

```{r, warning=FALSE}
#--------
# centrality indices
centRes <- centrality(Graph_lasso)

# Node strength (degree):
centRes$OutDegree # Or InDegree, it's the same in unweighted networks

o<-sort(centRes$OutDegree,decreasing = TRUE)[1:20]
cbind(t(statsclusters[1,names(o)]),as.numeric(o))

# Closeness:
centRes$Closeness

b<-sort(centRes$Closeness,decreasing = TRUE)[1:20]
cbind(t(statsclusters[1,names(b)]),as.numeric(b))
      
# Betweenness:
centRes$Betweenness

# print biggest betweenness
a<-sort(centRes$Betweenness,decreasing = TRUE)[1:20]
cbind(t(statsclusters[1,names(a)]),as.numeric(a))

centralityPlot(Graph_lasso)

```

# Comparing PCOR and LASSO
```{r, warning=FALSE}
Layout <- averageLayout(Graph_pcor,Graph_lasso)
layout(t(1:2))
qgraph(corMat, graph = "pcor", layout = Layout, threshold = "bonferroni",
       sampleSize = nrow(parcial), minimum = 0,
       cut = 0.15, maximum = 1, details = TRUE,
       esize = 20, title = "Partial correlations")

qgraph(corMat, graph = "glasso", layout = Layout, tuning = 0.3,
       sampleSize = nrow(parcial), minimum = 0,
       cut = 0.15, maximum = 1, details = TRUE,
       esize = 20, title = "LASSO regularization")

layout(1)
```

